A Variant of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus \\ (Draft)

### 2015-01-02 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
Rename folder with paper about Hajek and Anderson controversy
Fix calculus

% \s\s\s\s
% \infer[\pos_I]{\pos A}{w: \fbox{\infer*{A}{}} }
% \s\s\s\s\s
% \infer[\pos_E]{\omega: \fbox{ \infer*{}{A} } }{\pos A}

@@

\begin{center}
\textbf{eigen-box condition:}\\ 
$\omega$ must be a fresh name for a box. \\
\vspace{0.5em}
\textbf{boxed assumption condition:} \\
assumptions should be discharged within the box where they are made.
\end{center}

@@

Adding the modal rules results in a calculus that is suitable for the basic normal modal logic K.
In other words, {\NDK} is sound and complete relative to {\ND} extended with axiom K ($\nec(A\imp B)\imp (\nec A\imp \nec B)$) and the necessitation rule (which establishes that $\nec A$ is a theorem if $A$ is a theorem).

@@

>>>>

\s\s\s\s
\infer[\pos_I]{\pos A}{w: \fbox{\infer*{A}{}} }
\s\s\s\s
\infer[\pos_E]{\omega: \fbox{ \infer*{}{A} } }{\pos A}

@@

\begin{center}
\textbf{eigen-box condition:}\\ 
$\nec_I$ and $\pos_E$ are \emph{strong} modal rules: \\
$\omega$ must be a fresh name for the box they access \\ 
(in analogy to the eigen-variable condition for strong quantifier rules). \\
Every box must be accessed by \emph{exactly one} strong modal inference. \\
\vspace{0.5em}
\textbf{boxed assumption condition:} \\
assumptions should be discharged within the box where they are created.
\end{center}

@@

Adding the modal rules results in a calculus that is suitable for the basic normal modal logic \textbf{K}.
In other words, {\NDK} is sound and complete relative to {\ND} extended with axiom K ($\nec(A\imp B)\imp (\nec A\imp \nec B)$) and the necessitation rule (which establishes that $\nec A$ is a theorem if $A$ is a theorem).

@@

Without the restriction that every box must be accessed by exactly one strong modal inference, the calculus would be unsound for the modal logic \textbf{K}, because the formula $\all \psi. (\nec \psi \imp \pos \psi)$ would be derivable although it is not valid in \textbf{K}.

ToDo: show example of unsound derivation.
